---
title: "R_Markdown"
author: "Christopher_Zdyrski"
date: "3/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Data Summary
Get two original files

```{r}
fang_et_al_genotypes <- read.table('https://raw.githubusercontent.com/EEOB-BioData/BCB546-Spring2021/main/assignments/UNIX_Assignment/fang_et_al_genotypes.txt', header=TRUE, sep="\t",stringsAsFactors = FALSE)

snp_position <- read.table('https://raw.githubusercontent.com/EEOB-BioData/BCB546-Spring2021/main/assignments/UNIX_Assignment/snp_position.txt', header=TRUE, sep="\t", stringsAsFactors = FALSE)


```
###Attributes of fang_et_al_genotypes.txt

#This is my R Markdown document to analyze two snp files, combine them and pull out wanted data for further analysis in ggplot2. 

```{r}
dim(fang_et_al_genotypes)
```


#By inspecting this file I learned that:

#The file size is 6.1M.
#There are 2783 lines, 2744038 words and 11051939 bytes.
#There are 986 columns in this file.

###Attributes of snp_position.txt

```{r}
dim(snp_position)
file.size(snp_position, unit = "mb")
```

#By inspecting this file I learned that:

#The file size is 38K.
#There are 983 lines, 13198 words and 82763 bytes.
#There are 15 columns in this file.

###Data processing

#Install & load packages
```{r}
install.packages("tidyverse")
install.packages("ggplot2")
install.packages("stringr")
library(ggplot2)
library(tidyr)
library(tidyverse)
library(dplyr)
library(stringr)

```

#Seperate out teosinte (ZMPBA, ZMPIL, and ZMPJA) and maize (ZMMIL OR ZMMLR OR ZMMMR) with grep, and also get rid of column two and three 

```{r}

teosinte_data <- fang_et_al_genotypes[grep("ZMP", fang_et_al_genotypes$Group), ]
maize_data <- fang_et_al_genotypes[grep("ZMM", fang_et_al_genotypes$Group), ]


teosinte_data_excluding_col <- select(teosinte_data, -JG_OTU, -Group)

teosinte_data_excluding_col <- as_tibble(teosinte_data_excluding_col)

maize_data_excluding_col <- select(maize_data, -JG_OTU, -Group)

maize_data_excluding_col <- as_tibble(maize_data_excluding_col)

```

#Swap names

```{r}

swap_teosinte_data_excluding_col <- column_to_rownames(teosinte_data_excluding_col, var="Sample_ID")

swap_maize_data_excluding_col <- column_to_rownames(maize_data_excluding_col, var="Sample_ID")
```


#Transpose both genotype files to swap the rows and columns

```{r}

transposed_teosinte_data <- t(swap_teosinte_data_excluding_col)
transposed_maize_data <- t(swap_maize_data_excluding_col)


transposed_teosinte_data <- rownames_to_column(as.data.frame(transposed_teosinte_data), var = "SNP_ID")
transposed_maize_data <- rownames_to_column(as.data.frame(transposed_maize_data), var = "SNP_ID")

```


#Crop and Sort snp file
```{r}
snp_cropped <- select(snp_position, SNP_ID, Chromosome, Position)

attach(snp_cropped)
sorted_snp_position <- snp_cropped[order(SNP_ID),]
```

#Merge files (maize/teosinte with snp_position file)
```{r}
teosinte_joined <- merge(sorted_snp_position, transposed_teosinte_data, by="SNP_ID")

maize_joined <- merge(sorted_snp_position, transposed_maize_data, by="SNP_ID")

```




###Teosinte Awk out all the 20 files
```{r}

teosinte_chrom_1.txt <- teosinte_joined[grep("1$", teosinte_joined$Chromosome), ]
teosinte_chrom_2.txt <- teosinte_joined[grep("2$", teosinte_joined$Chromosome), ]
teosinte_chrom_3.txt <- teosinte_joined[grep("3$", teosinte_joined$Chromosome), ]
teosinte_chrom_4.txt <- teosinte_joined[grep("4$", teosinte_joined$Chromosome), ]
teosinte_chrom_5.txt <- teosinte_joined[grep("5$", teosinte_joined$Chromosome), ]
teosinte_chrom_6.txt <- teosinte_joined[grep("6$", teosinte_joined$Chromosome), ]
teosinte_chrom_7.txt <- teosinte_joined[grep("7$", teosinte_joined$Chromosome), ]
teosinte_chrom_8.txt <- teosinte_joined[grep("8$", teosinte_joined$Chromosome), ]
teosinte_chrom_9.txt <- teosinte_joined[grep("9$", teosinte_joined$Chromosome), ]
teosinte_chrom_10.txt <- teosinte_joined[grep("10", teosinte_joined$Chromosome), ]

```



###Teosinte make 2 files, one with the 3 headers, and another to gsub out the "?" then cbind them together
```{r}
teosinte_chrom_1_hyphen.txt <- teosinte_chrom_1.txt
ncol(teosinte_chrom_1_hyphen.txt)
teosinte_chrom_1_hyphen.txt <- apply(teosinte_chrom_1_hyphen.txt[,4:978], 2, function(teosinte_chrom_1_hyphen.txt) gsub("\\?", "-", teosinte_chrom_1_hyphen.txt))

teosinte_chrom_1.txt_three_col <- teosinte_chrom_1.txt[1:3]
teosinte_chrom_1_hyphen.txt <- cbind(teosinte_chrom_1.txt_three_col, teosinte_chrom_1_hyphen.txt)
```
```{r}
teosinte_chrom_2_hyphen.txt <- teosinte_chrom_2.txt
ncol(teosinte_chrom_2_hyphen.txt)
teosinte_chrom_2_hyphen.txt <- apply(teosinte_chrom_2_hyphen.txt[,4:978], 2, function(teosinte_chrom_2_hyphen.txt) gsub("\\?", "-", teosinte_chrom_2_hyphen.txt))

teosinte_chrom_2.txt_three_col <- teosinte_chrom_2.txt[1:3]
teosinte_chrom_2_hyphen.txt <- cbind(teosinte_chrom_2.txt_three_col, teosinte_chrom_2_hyphen.txt)
```

```{r}
teosinte_chrom_3_hyphen.txt <- teosinte_chrom_3.txt
ncol(teosinte_chrom_3_hyphen.txt)
teosinte_chrom_3_hyphen.txt <- apply(teosinte_chrom_3_hyphen.txt[,4:978], 2, function(teosinte_chrom_3_hyphen.txt) gsub("\\?", "-", teosinte_chrom_3_hyphen.txt))

teosinte_chrom_3.txt_three_col <- teosinte_chrom_3.txt[1:3]
teosinte_chrom_1_hyphen.txt <- cbind(teosinte_chrom_1.txt_three_col, teosinte_chrom_1_hyphen.txt)
```

```{r}
teosinte_chrom_4_hyphen.txt <- teosinte_chrom_4.txt
ncol(teosinte_chrom_4_hyphen.txt)
teosinte_chrom_4_hyphen.txt <- apply(teosinte_chrom_4_hyphen.txt[,4:978], 2, function(teosinte_chrom_4_hyphen.txt) gsub("\\?", "-", teosinte_chrom_4_hyphen.txt))

teosinte_chrom_4.txt_three_col <- teosinte_chrom_4.txt[1:3]
teosinte_chrom_4_hyphen.txt <- cbind(teosinte_chrom_4.txt_three_col, teosinte_chrom_4_hyphen.txt)
```

```{r}
teosinte_chrom_5_hyphen.txt <- teosinte_chrom_5.txt
ncol(teosinte_chrom_5_hyphen.txt)
teosinte_chrom_5_hyphen.txt <- apply(teosinte_chrom_5_hyphen.txt[,4:978], 2, function(teosinte_chrom_5_hyphen.txt) gsub("\\?", "-", teosinte_chrom_5_hyphen.txt))

teosinte_chrom_5.txt_three_col <- teosinte_chrom_5.txt[1:3]
teosinte_chrom_5_hyphen.txt <- cbind(teosinte_chrom_5.txt_three_col, teosinte_chrom_5_hyphen.txt)
```

```{r}
teosinte_chrom_6_hyphen.txt <- teosinte_chrom_6.txt
ncol(teosinte_chrom_6_hyphen.txt)
teosinte_chrom_6_hyphen.txt <- apply(teosinte_chrom_6_hyphen.txt[,4:978], 2, function(teosinte_chrom_6_hyphen.txt) gsub("\\?", "-", teosinte_chrom_6_hyphen.txt))

teosinte_chrom_6.txt_three_col <- teosinte_chrom_6.txt[1:3]
teosinte_chrom_6_hyphen.txt <- cbind(teosinte_chrom_6.txt_three_col, teosinte_chrom_6_hyphen.txt)
```

```{r}
teosinte_chrom_7_hyphen.txt <- teosinte_chrom_7.txt
ncol(teosinte_chrom_7_hyphen.txt)
teosinte_chrom_7_hyphen.txt <- apply(teosinte_chrom_7_hyphen.txt[,4:978], 2, function(teosinte_chrom_7_hyphen.txt) gsub("\\?", "-", teosinte_chrom_7_hyphen.txt))

teosinte_chrom_7.txt_three_col <- teosinte_chrom_7.txt[1:3]
teosinte_chrom_7_hyphen.txt <- cbind(teosinte_chrom_7.txt_three_col, teosinte_chrom_7_hyphen.txt)
```

```{r}
teosinte_chrom_8_hyphen.txt <- teosinte_chrom_8.txt
ncol(teosinte_chrom_8_hyphen.txt)
teosinte_chrom_8_hyphen.txt <- apply(teosinte_chrom_8_hyphen.txt[,4:978], 2, function(teosinte_chrom_8_hyphen.txt) gsub("\\?", "-", teosinte_chrom_8_hyphen.txt))

teosinte_chrom_8.txt_three_col <- teosinte_chrom_8.txt[1:3]
teosinte_chrom_8_hyphen.txt <- cbind(teosinte_chrom_8.txt_three_col, teosinte_chrom_8_hyphen.txt)
```

```{r}
teosinte_chrom_9_hyphen.txt <- teosinte_chrom_9.txt
ncol(teosinte_chrom_9_hyphen.txt)
teosinte_chrom_9_hyphen.txt <- apply(teosinte_chrom_9_hyphen.txt[,4:978], 2, function(teosinte_chrom_9_hyphen.txt) gsub("\\?", "-", teosinte_chrom_9_hyphen.txt))

teosinte_chrom_9.txt_three_col <- teosinte_chrom_9.txt[1:3]
teosinte_chrom_9_hyphen.txt <- cbind(teosinte_chrom_9.txt_three_col, teosinte_chrom_9_hyphen.txt)
```

```{r}
teosinte_chrom_10_hyphen.txt <- teosinte_chrom_10.txt
ncol(teosinte_chrom_10_hyphen.txt)
teosinte_chrom_10_hyphen.txt <- apply(teosinte_chrom_10_hyphen.txt[,4:978], 2, function(teosinte_chrom_10_hyphen.txt) gsub("\\?", "-", teosinte_chrom_10_hyphen.txt))

teosinte_chrom_10.txt_three_col <- teosinte_chrom_10.txt[1:3]
teosinte_chrom_10_hyphen.txt <- cbind(teosinte_chrom_10.txt_three_col, teosinte_chrom_10_hyphen.txt)
```

###Maize Awk out all the 20 files
```{r}
maize_chrom_1.txt <- maize_joined[grep("1$", maize_joined$Chromosome), ]
maize_chrom_2.txt <- maize_joined[grep("2$", maize_joined$Chromosome), ]
maize_chrom_3.txt <- maize_joined[grep("3$", maize_joined$Chromosome), ]
maize_chrom_4.txt <- maize_joined[grep("4$", maize_joined$Chromosome), ]
maize_chrom_5.txt <- maize_joined[grep("5$", maize_joined$Chromosome), ]
maize_chrom_6.txt <- maize_joined[grep("6$", maize_joined$Chromosome), ]
maize_chrom_7.txt <- maize_joined[grep("7$", maize_joined$Chromosome), ]
maize_chrom_8.txt <- maize_joined[grep("8$", maize_joined$Chromosome), ]
maize_chrom_9.txt <- maize_joined[grep("9$", maize_joined$Chromosome), ]
maize_chrom_10.txt <- maize_joined[grep("10", maize_joined$Chromosome), ]

```

###maize make 2 files, one with the 3 headers, and another to gsub out the "?" then cbind them together
```{r}
maize_chrom_1_hyphen.txt <- maize_chrom_1.txt
ncol(maize_chrom_1_hyphen.txt)
maize_chrom_1_hyphen.txt <- apply(maize_chrom_1_hyphen.txt[,4:978], 2, function(maize_chrom_1_hyphen.txt) gsub("\\?", "-", maize_chrom_1_hyphen.txt))

maize_chrom_1.txt_three_col <- maize_chrom_1.txt[1:3]
maize_chrom_1_hyphen.txt <- cbind(maize_chrom_1.txt_three_col, maize_chrom_1_hyphen.txt)
```
```{r}
maize_chrom_2_hyphen.txt <- maize_chrom_2.txt
ncol(maize_chrom_2_hyphen.txt)
maize_chrom_2_hyphen.txt <- apply(maize_chrom_2_hyphen.txt[,4:978], 2, function(maize_chrom_2_hyphen.txt) gsub("\\?", "-", maize_chrom_2_hyphen.txt))

maize_chrom_2.txt_three_col <- maize_chrom_2.txt[1:3]
maize_chrom_2_hyphen.txt <- cbind(maize_chrom_2.txt_three_col, maize_chrom_2_hyphen.txt)
```

```{r}
maize_chrom_3_hyphen.txt <- maize_chrom_3.txt
ncol(maize_chrom_3_hyphen.txt)
maize_chrom_3_hyphen.txt <- apply(maize_chrom_3_hyphen.txt[,4:978], 2, function(maize_chrom_3_hyphen.txt) gsub("\\?", "-", maize_chrom_3_hyphen.txt))

maize_chrom_3.txt_three_col <- maize_chrom_3.txt[1:3]
maize_chrom_1_hyphen.txt <- cbind(maize_chrom_1.txt_three_col, maize_chrom_1_hyphen.txt)
```

```{r}
maize_chrom_4_hyphen.txt <- maize_chrom_4.txt
ncol(maize_chrom_4_hyphen.txt)
maize_chrom_4_hyphen.txt <- apply(maize_chrom_4_hyphen.txt[,4:978], 2, function(maize_chrom_4_hyphen.txt) gsub("\\?", "-", maize_chrom_4_hyphen.txt))

maize_chrom_4.txt_three_col <- maize_chrom_4.txt[1:3]
maize_chrom_4_hyphen.txt <- cbind(maize_chrom_4.txt_three_col, maize_chrom_4_hyphen.txt)
```

```{r}
maize_chrom_5_hyphen.txt <- maize_chrom_5.txt
ncol(maize_chrom_5_hyphen.txt)
maize_chrom_5_hyphen.txt <- apply(maize_chrom_5_hyphen.txt[,4:978], 2, function(maize_chrom_5_hyphen.txt) gsub("\\?", "-", maize_chrom_5_hyphen.txt))

maize_chrom_5.txt_three_col <- maize_chrom_5.txt[1:3]
maize_chrom_5_hyphen.txt <- cbind(maize_chrom_5.txt_three_col, maize_chrom_5_hyphen.txt)
```

```{r}
maize_chrom_6_hyphen.txt <- maize_chrom_6.txt
ncol(maize_chrom_6_hyphen.txt)
maize_chrom_6_hyphen.txt <- apply(maize_chrom_6_hyphen.txt[,4:978], 2, function(maize_chrom_6_hyphen.txt) gsub("\\?", "-", maize_chrom_6_hyphen.txt))

maize_chrom_6.txt_three_col <- maize_chrom_6.txt[1:3]
maize_chrom_6_hyphen.txt <- cbind(maize_chrom_6.txt_three_col, maize_chrom_6_hyphen.txt)
```

```{r}
maize_chrom_7_hyphen.txt <- maize_chrom_7.txt
ncol(maize_chrom_7_hyphen.txt)
maize_chrom_7_hyphen.txt <- apply(maize_chrom_7_hyphen.txt[,4:978], 2, function(maize_chrom_7_hyphen.txt) gsub("\\?", "-", maize_chrom_7_hyphen.txt))

maize_chrom_7.txt_three_col <- maize_chrom_7.txt[1:3]
maize_chrom_7_hyphen.txt <- cbind(maize_chrom_7.txt_three_col, maize_chrom_7_hyphen.txt)
```

```{r}
maize_chrom_8_hyphen.txt <- maize_chrom_8.txt
ncol(maize_chrom_8_hyphen.txt)
maize_chrom_8_hyphen.txt <- apply(maize_chrom_8_hyphen.txt[,4:978], 2, function(maize_chrom_8_hyphen.txt) gsub("\\?", "-", maize_chrom_8_hyphen.txt))

maize_chrom_8.txt_three_col <- maize_chrom_8.txt[1:3]
maize_chrom_8_hyphen.txt <- cbind(maize_chrom_8.txt_three_col, maize_chrom_8_hyphen.txt)
```

```{r}
maize_chrom_9_hyphen.txt <- maize_chrom_9.txt
ncol(maize_chrom_9_hyphen.txt)
maize_chrom_9_hyphen.txt <- apply(maize_chrom_9_hyphen.txt[,4:978], 2, function(maize_chrom_9_hyphen.txt) gsub("\\?", "-", maize_chrom_9_hyphen.txt))

maize_chrom_9.txt_three_col <- maize_chrom_9.txt[1:3]
maize_chrom_9_hyphen.txt <- cbind(maize_chrom_9.txt_three_col, maize_chrom_9_hyphen.txt)
```

```{r}
maize_chrom_10_hyphen.txt <- maize_chrom_10.txt
ncol(maize_chrom_10_hyphen.txt)
maize_chrom_10_hyphen.txt <- apply(maize_chrom_10_hyphen.txt[,4:978], 2, function(maize_chrom_10_hyphen.txt) gsub("\\?", "-", maize_chrom_10_hyphen.txt))

maize_chrom_10.txt_three_col <- maize_chrom_10.txt[1:3]
maize_chrom_10_hyphen.txt <- cbind(maize_chrom_10.txt_three_col, maize_chrom_10_hyphen.txt)
```


###Maize Unknown SNPs
Multiple Position SNPs
```{r}

```

###Teosinte Unknown SNPs
Multiple Position SNPs

```{r}

```


##ggplot step
#Use pivot longer to neaten up data for ggplot input

```{r}
pivot_longer()

```

#Here is my plot
```{r}
ggplot()

```
