---
title: "R_Markdown"
author: "Christopher_Zdyrski"
date: "3/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Summary

###Attributes of fang_et_al_genotypes.txt

This is my R Markdown document to analyze two snp files, combine them and pull out wanted data for further analysis in ggplot2. 

```{r fang_et_al_genotypes}
dim(fang_et_al_genotypes)
```


By inspecting this file I learned that:

The file size is 6.1M.
There are 2783 lines, 2744038 words and 11051939 bytes.
There are 986 columns in this file.

###Attributes of snp_position.txt

```{r snp_position}
dim(snp_position)
```

By inspecting this file I learned that:

The file size is 38K.
There are 983 lines, 13198 words and 82763 bytes.
There are 15 columns in this file.

##Data processing
Seperate out teosinte (ZMPBA, ZMPIL, and ZMPJA) and maize (ZMMIL OR ZMMLR OR ZMMMR )

```
head(fang_et_al_genotypes)

```

Put header of the genotype file into its own file for use later


Add headers to both teosinte and maize genotype files



Transpose both genotype files to swap the rows and columns

```
transposed_teosinte_with_header <- t(teosinte_with_header)
```

Sort genotpye and snp file based off column 1, "SNP_ID"


Sort genotpye and snp file based off column 1, "SNP_ID"


Join files together to combine the SNP ID and the genotype


###Teosinte Awk out all the 40 files Then use setd to change "?" to "-"



###Maize Awk out all the 40 files Then use setd to change "?" to "-"


###Maize Unknown SNPs


Multiple Position SNPs


###Teosinte Unknown SNPs


Multiple Position SNPs




##ggplot

Load tidyverse

```
install.packages("tidyverse")
library(tidyr)
```

Use pivot longer to neaten up data
```
pivot_longer()
```

Here is my plot

```{r pressure, echo=FALSE}
plot(pressure)
```
